Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-24 paper.tex
update

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm using a set of binary strings as individuals, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions with functional correctness. In particularly, a greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, The finding is supported by our first comparison experiment.

Few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} employ EC technique for considering both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ Genetic Algorithm for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic. This evaluation method takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but different semantic matchmaking types are ignored in the evaluation model. The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured by the similarity using information retrieval technique.

>>>>

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimization and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal QoS. However, there exists a scalability problem for the enumeration technique. EC techniques are used to automatically generate solutions with optimal QoS, which is considered to a NP-hard problem. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by \cite{yu2013adaptive} to find optimal solutions, which is reached by penalising infeasible solutions using a fitness function. A hybird approach employs both greedy search algorithm and GP is introduced in \cite{ma2015hybrid} to generate solutions that are functionally correct. In particularly, greedy search techniques have been used to generate directed acyclic graphs (DAGs) as composition solutions that is further transferred to tree structures for initialisation and mutation. To eliminating the transformation process from DAGs, a promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG-based solution. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality, which could lead to too specific outputs produced by the selected services, and this finding is supported by our first comparison experiment.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ GA for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic. This evaluation model takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but . The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured by the similarity using information retrieval technique.
